Har en persons høyde innvirkning på lønnen?

### 2020-10-11 MSB105-Assignment-2-Katrine-Karl-Gunnar.Rmd
pdf commit

---
title: "Har en persons høyde innvirkning på lønnen?"
subtitle: "Assignment 2 i MSB105 Data Science - innleveringsfrist 12.10.20"
author: 
  - Katrine Hope
  - Karl-Gunnar Severinsen
classoption: twoside
fontsize: 12pt
linestretch: 1.5
output:
  html_document:
    df_print: paged
    toc: true
    toc_depth: 3
    toc_float: true
  pdf_document:
    df_print: paged
    toc: true
    toc_depth: 3
    fig_height: 4
---

>>>>

---
title: "Har en persons høyde innvirkning på lønnen?"
subtitle: "Assignment 2 i MSB105 Data Science - innleveringsfrist 12.10.20"
author: 
  - Katrine Hope
  - Karl-Gunnar Severinsen
classoption: twoside
fontsize: 12pt
linestretch: 1.5
output:
  pdf_document:
    df_print: paged
    toc: true
    toc_depth: 3
    fig_height: 4
  html_document:
    df_print: paged
    toc: true
    toc_depth: 3
    toc_float: true
---
